Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-31 parts/sa.tex
new graph definition

The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
  \end{align*}
\end{definition}

\begin{definition}[Coherent solution]
\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}

\begin{theorem}[Under-Approximation]
\label{th:approxinf}
  If the graph $\cwB$ contains no cycle,
  all objectives have at least one solution
  and all cooperative sort requisites are coherent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}

>>>>

The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}

@@

\begin{comment}
\begin{definition}
  $\cwB = (\V, \E)$, $V \subset \PHproc \cup \Obj \cup \powerset(\PHproc)$ and $E \subset V \times V$
  so that:\\
  $\w \subset \V$\\
  $\{ \PHbounce(P) \mid P \in \V \} \subset \V$\\
  $\{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} \subset \E$\\ % Sol
  $\{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} \subset \V$\\
  $\{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} \subset \E$\\ % Sol
  $\{ a_i \in \PHproc \mid (ps, a_i) \in \E \} \subset \V$\\
  $\{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} \subset \E$\\ % Req
  $\{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} \subset \V$\\
  $\{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} \subset \E$\\ % Cont
  $\{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} \subset \E$\\ % ReqSolPrio
\end{definition}

\begin{definition}
  $\cwB = (\V, \E)$, $V \subset \PHproc \cup \Obj \cup \powerset(\PHproc)$ and $E \subset V \times V$
  so that:
  \begin{align*}
    \w &\subset \V\\
    \{ \PHbounce(P) \mid P \in \V \} &\subset \V\\
    \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
    \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
    \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
    \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E % ReqSolPrio
  \end{align*}
\end{definition}
\end{comment}

\newcommand{\V}{V}
\newcommand{\E}{E}
\newcommand{\cwV}{\V_\ctx^\w}
\newcommand{\cwE}{\E_\ctx^\w}
\newcommand{\VProc}{\V_\PHproc}
\newcommand{\VObj}{\V_\Obj}
\newcommand{\VSol}{\V_{Sol}}

\def\Bv{\sat{\cwV}}
\def\Be{\sat{\cwE}}

\begin{definition}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \powerset(\PHproc)$ and $\cwE \subset \cwV \times \cwV$ so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
  \end{align}
\end{definition}

\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$,
\pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains and
\pref{eq:EReq} links a required process $a_i$ of a component to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$.
If the resolution of an objective $P$ may require a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
Finally, \pref{eq:EPrio} links a required process $a_i$ of a cooperative sorts to its solutions in $\csState(a_i)$.

\begin{comment}
\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
  \end{align*}
\end{definition}

\begin{definition}[Coherent solution]
\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}
\end{comment}

\begin{definition}[Coherent solution]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said coherent if and only if
  it does not belong to $(\PHproc \times \powerset(\PHproc))$
  or if it does and $y$ has no process successor $a_j \in \Bv \cap \PHproc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
%  A set of processes $ps \in \Bv \cap \powerset(\PHproc)$ is said coherent if and only if
%  it has no process successor $a_j \in \Bv \cap \PHproc$ so that there exists $a_i \in ps$, $a_i \neq a_k$.
\end{definition}

\begin{theorem}[Under-Approximation]
\label{th:approxinf}
  If the graph $\cwB$ contains no cycle,
  all objectives have at least one solution
  and all edges are coherent,
  %and $\forall (a_i, ps) \in \cwE \cap (\Proc \times \powerset(\PHproc))$, $ps$ is coherent,
  %and all cooperative sort requisites are coherent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}
